FAIR Theory: Applying Open Science Principles to the Construction and Iterative Improvement of Scientific Theories

### 2024-12-12 manuscript.Rmd
Update manuscript.Rmd

The FAIR Guiding Principles (hereafter: FAIR principles) were established to make research data more Findable, Accessible, Interoperable and Reusable [REF].
Since their inception, scholars have demonstrated their relevance for making other information artefacts more open.
This paper argues that the FAIR principles can advance effective and transparent scholarly communication about theory.
To this end, we introduce "FAIR theory":
a digital representation of theory, compliant with the FAIR principles.
By improving the efficiency of scholarly communication, FAIR Theory has the potential to accelerate cumulative knowledge acquisition and advance social scientific research.

>>>>

The FAIR Guiding Principles (hereafter: FAIR principles) were established to improve the reusability of research data by making them more findable, accessible, interoperable and reusable [REF] for both humans and computers.
Since their inception in 2014, scholars have demonstrated their relevance for making other information artefacts more open, such as research software [@lamprecht2020towards; @barker2022introducing], computational workflows [@wilkinson2024applying] or simulation studies [@amaro2024need].
This paper argues that the FAIR principles can advance effective and transparent scholarly communication about theory.
To this end, we introduce "FAIR theory":
a digital representation of a scientific theory, compliant with the FAIR principles.
By improving the efficiency of scholarly communication, FAIR Theory has the potential to foster and accelerate cumulative knowledge acquisition and ultimately advance social scientific research.
